---
title: "Lab 00 - Hello IDS!"
author: "Chinedu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data
test
```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("abdullah", "Aaron", "Tommy", 
           "Luyanda", "Chinedu"),
  github_username = c("abdullaS06", "aaronj2405", "tommys2626550", 
                      "LuyandaMadliwa", "chinedua26"), 
  colour = c("red", "blue", "red", 
             "red", "purple"),
  hobby = c("music", "running", "football", 
            "music", "running"),
  favourite_number = c(7, 8, 3, 6, 5)
  )

team_data
```
favourite colours and. numbers
### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


assigns x and y axis labels
### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "usernames", 
          y = "fav number",
          title = "teammates")
```
instead of count, use number of students. Use different colours for each bar. 
A pie chart could be used instead to show proportion.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
